Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
3

%\section{Running Example}
%\label{running-example}
\section{Common Vocabularies in SBE Sciences}
\label{rdf-representation}
\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}\tb{die vokabular-beschreibungen klarer strukturieren}
%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following. For three of them, we analyzed actual data according to constraint violations. For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.\tb{müssen wir auch noch schreiben wieso wie keine DCAT daten validiert haben?}

%\textbf{Metadata on Aggregated Data.}
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
%\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}. 
%(e.g., the year in which \emph{formal childcare} has been determined).
\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen? Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}

@@

\tb{ 
klare, einfache struktur: 1. grundidee (constraints identifizieren, validieren auf datensets, zu belastbaren aussagen kommen für die weitere entwicklung von constraint languages)
2. vorstellung der untersuchten vokabulare
3. beschreiben, wo die constraints herkommen, bzw. wie die generiert wurden. dabei auch auf die klassifikation eingehen, aber nur im hinblick auf die spätere auswertung, nicht als main contribution des papers
4. evaluation mit beschreibung der datasets in setup (das les ich mir gleich mal durch, das hast du ja schon neu geschrieben)
ja, und dann prägnante conclusion mit zusammenfassung der hypothesen, der bedutung für die weitere entwicklung von CLs und natürlich future work
}

>>>>

%\section{Running Example}
%\label{running-example}
\section{Common Vocabularies in SBE Sciences}
\label{rdf-representation}

%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.

For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following. For three of them, we analyzed actual data according to constraint violations. For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.

%\textbf{Metadata on Aggregated Data.}
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
%\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}. 
%(e.g., the year in which \emph{formal childcare} has been determined).
%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen? Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}

@@
